---
title: "Boosting Insights"
output: 
  github_document:
    pandoc_args: --webtex
    html_preview: false
---

---


## Introduction

The following will test boosting capabilities to predict incomes given some sociodemographic variables. We will then compare boosting to other Machine Learning methods and try to understand the differences. 


## Exploratory Data Analyis

First of all, let us deep-dive in the dataset. 

```{r cars}
data <- read.csv("data/adult.data", header = F)
colnames(data) <- c("age", 
                    "workclass", 
                    "fnlwgt", 
                    "education", 
                    "education_num", 
                    "marital_status", 
                    "occupation", 
                    "relationship", 
                    "race", 
                    "sex", 
                    "capital_gain", 
                    "capital_loss", 
                    "hours_per_week", 
                    "native_contry", 
                    "income")
```




```{r cars_2}
plot(data$hours_per_week)
```

## Boosting Review

Boosting classifies values based on a weighted vote: $H(x)=sign(\sum_{t=1}^T\alpha_th_t(x))$
  



